MCC Simulations

### 2018-03-10 stats/simulations/mcc_kids_simulations.Rmd
kids data sim

```{r}
conditions <- read.csv("kids_condition_means.csv", sep=";")

generate_data <- function(condition_df, n_subs = 16, n_trials = 3) {
  tibble(count = condition_df$count,
         condition = condition_df$condition,
         age = condition_df$age,
         type = condition_df$type,
         correct = rbinom( n_subs * n_trials, 1,
                          condition_df$correct),
         subid = rep(1:n_subs, n_trials))
}

participant_data <- conditions %>%
  mutate(index = 1:n()) %>%
  split(.$index) %>%
  map_df(generate_data)%>%
  mutate(subid=paste(subid,age,condition,sep="_"))%>%
  arrange(condition, subid)

 participant_data %>%
  group_by(condition,age,type,subid) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct") %>%
  mutate(ciw = ci_upper-ci_lower) %>%
  group_by() %>%
  summarise(ciw = mean(ciw))%>%
  knitr::kable(digits = 3)

@@

@@

summary(lm)
drop1(lm, test = "Chisq")

>>>>

### condition means based on adult data with slightly smaller effect for younger kids

conditions <- tibble (
  age = c(rep(c(2,2,4,4),3)),
  condition = c(rep(c("pref"),4),rep(c("novel"),4),rep(c("inf"),4)),
  type = c(rep(c("test","ctrl"),6)),
  correct = c(0.8666667,0.5416667,0.9666667,0.6416667,0.7333333,0.4916667,0.8333333,0.5916667,0.6716667,0.5,0.7416667,0.4583333)
)

generate_data <- function(condition_df, n_subs = 16, n_trials = 3) {
  tibble(condition = condition_df$condition,
         age = condition_df$age,
         type = condition_df$type,
         correct = rbinom( n_subs * n_trials, 1,
                          condition_df$correct),
         subid = rep(1:n_subs, n_trials))
}

### Average CI width across all condition, type and agegroup combinations.
### For adults (n = 40), this average CI width 0.172
### Average CI width as function of n kids: 12 = 0.261; 16 = 0.231; 24 = 0.192; 30 = 0.174; 40 = 0.150

for (i in 1:100) {
x[i] = conditions %>%
  mutate(index = 1:n()) %>%
  split(.$index) %>%
  map_df(generate_data)%>%
  mutate(subid=paste(subid,age,condition,sep="_"))%>%
  arrange(condition, subid) %>%
  group_by(condition,age,type,subid) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct") %>%
  mutate(ciw = ci_upper-ci_lower) %>%
  group_by() %>%
  summarise(ciw = mean(ciw))%>%
  pull()
}

mean(unlist(x))

@@

participant_data <- conditions %>%
  mutate(index = 1:n()) %>%
  split(.$index) %>%
  map_df(generate_data)%>%
  mutate(subid=paste(subid,age,condition,sep="_"))

@@

summary(lm)
